User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R memory models of tag retrieval

### 2013-10-10 writeups/proposal/proposal.tex
foo
Former-commit-id: 1697063aef3d7eb3a3409f079809c3963ecc6c03 [formerly 600eef6d1b8808e2ca402441cd51361bb7b6c565]
Former-commit-id: be434b9b216f72183faed8e600ff25830845ce23

Vector-based and LSA retrieval models calculate chunk activation by correlating a representation of the current context with each memory item.
Bayesian retrieval models like ACT-R calculate activation by computing each chunk's posterior odd adjustment likelihood, given the context.
These two computations are certainly not equivalent, even though they are most likely highly correlated with one another.
It may be interesting to explore how model performance changes when one calculation is swapped out for another.
For example, a vector-based model could generate a compressed (reduced dimension) co-occurrence matrix, and then Bayesian calculations could be performed on that matrix to compute adjusted odd likelihoods.
Alternatively, a vector representation of the current context could be correlated with each column in a full co-occurrence matrix.
It's unlikely that the latter technique will improve performance, as \textcite{Landauer1997} has shown that performing correlations on uncompressed co-occurrence matrices does not perform well.
But it may be the case that using Bayesian computation on a compressed vector-based model improves performance.

>>>>

Vector-based and LSA retrieval models calculate chunk activation by correlating a representation of the current context with each memory item.
Bayesian retrieval models like ACT-R calculate activation by computing each chunk's posterior odd adjustment likelihood, given the context.
These two computations are certainly not equivalent, even though they are most likely highly correlated with one another.
It may be interesting to explore how model performance changes when one calculation is swapped out for another.
For example, a vector-based model could generate a compressed (reduced dimension) co-occurrence matrix, and then Bayesian calculations could be performed on that matrix to compute adjusted odd likelihoods.
Alternatively, a vector representation of the current context could be correlated with each column in a full co-occurrence matrix.
It is unlikely that the latter technique will improve performance, as \textcite{Landauer1997} has shown that performing correlations on uncompressed co-occurrence matrices does not perform well.
But it may be the case that using Bayesian computation on a compressed vector-based model improves performance.
